Word learning at the semantics pragmatics interface

### 2020-03-31 paper/visualizations.Rmd
work on MHs comments

---
title: "Word learning at the semantics pragmatics interface"
subtitle: "Supplementary material"
author: "Manuel Bohn, Michael Henry Tessler and Michael C. Frank"
output: 
  bookdown::html_document2:
    toc: yes
    toc_float: true
    fig_caption: yes
    code_folding: hide
    number_sections: false
bibliography: library.bib
#csl: pnas.csl
header-includes:
  \usepackage{caption}
  \renewcommand{\thetable}{S\arabic{table}} 
  \renewcommand{\thefigure}{S\arabic{figure}}
---

```{r, include = F}
library(tidyverse)
library(rwebppl)
library(brms)
library(coda)
library(ggthemes)
library(readxl)
library(ggpubr)
library(stringr)
library(matrixStats)
library(data.table)
library(langcog)
library(ggimage)
library(BayesFactor)

@@

# Overview

The goal of this study is to investigate the integration of semantic and pragmatic information during word learning in children between 2 and 5 years of age. As a first step, we replicate earlier work showing that children rely on different forms of pragmatic and semantic information during word learning. In experiment 1, we show that children make a so called mutual exclusivity inference and that this inference depends on children's developing semantic knowledge. In a second experiment, we show that children make inferences about word meanings based on common ground. In a third experiment, we find that, when combined in one procedure, children are sensitive to the way that the two inferences are aligned.

Next, we introduce a computational framework which we use to formalize the process of how the inferences are integrated. As a part of this, we identify three information sources that children consider when making the alleged inferences: semantic knowledge, expectations about speaker informativeness and sensitivity to common ground. We then use the our modelling framework to ask which of these information sources are necessary to predict children's responses in experiment 3.

In the final section, we turn to the process by which information is integrated. We contrast the process of rational Bayesian inference we introduced in our model with a biased integration process in which one type of inference is given more weight. As part of this, we also explore alternative ways to think about developmental change in the integration process.

# Empirical studies

## Experiment 1: Mutual exclusivity

The first experiment tested the so called mutual exclusivity inference in children between 2 and 5 years of age. The general phenomena is that when presented with a familiar and an unfamiliar object, children expect a novel word to refer to the unfamiliar object [e.g. @markman1988children]. A range of explanations have been put forward for the cognitive basis of this inference [see @lewis2020-me for a discussion]. Here, we treat the mutual exclusivity inference as pragmatic [e.g. @clark1987principle]. The inference process is specified in the model below.

The first goal of this experiment was to quantify developmental change in the age range tested. The second goal was to test the role of semantic knowledge [cf. @lewis2020-me]. The assumption is that the strength of the mutual exclusivity inference varies with knowledge of the word for the familiar object. That is, when the familiar object is an object for which children are less likely to know the word, they are less likely to assume that the novel word refers to the unfamiliar object. To test this, we systematically varied the familiar object that were presented alongside the novel object.

The experiment was preregistered at https://osf.io/gy37b. The experiment itself can be run by downloading the associated repository and opening the file `experiments/kids/kids_me.html`.

### Participants

We tested a total number of `r length(unique(me_data$subid))` children, including `r length(unique(me_data$subid[me_data$subage == 2]))` 2-year-olds (range = `r format(round(min(me_data$age_num[me_data$subage == 2]),2), nsmall = 2)` - `r format(round(max(me_data$age_num[me_data$subage == 2]),2), nsmall = 2)`, 15 girls), `r length(unique(me_data$subid[me_data$subage == 3]))` 3-year-olds (range = `r format(round(min(me_data$age_num[me_data$subage == 3]),2), nsmall = 2)` - `r format(round(max(me_data$age_num[me_data$subage == 3]),2), nsmall = 2)`, 22 girls) and  `r length(unique(me_data$subid[me_data$subage == 4]))` 4-year-olds (range = `r format(round(min(me_data$age_num[me_data$subage == 4]),2), nsmall = 2)` - `r format(round(max(me_data$age_num[me_data$subage == 4]),2), nsmall = 2)`, 16 girls). Data from 10 additional children was not included because they were either exposed to less than 75% of English at home (5), did not finish at least half of the test trials (2), the technical equipment failed (2) or their parents reported an autism spectrum disorder (1). All children were recruited from the floor of a Children’s museum in San José, California, USA. This population is characterized by diverse ethnic background (predominantly White, Asian, or mixed ethnicity) and high levels of parental education and socioeconomic status. Parents consented to their children’s participation and provided demographic information. All experiments were approved by the Stanford Institutional Review Board (protocol no. 19960).

### Procedure

The experiment was presented as an interactive picture book on a tablet computer [@frank2016using]. Figure \@ref(fig:fig1)A shows the general setup. Children saw an animal standing on a little hill between two tables. For each animal character, we recorded a set of utterances (one native English speaker per animal) that were used to make requests. Each experiment started with two training trials in which the speaker requested known objects (car and ball).

In experiment 1, on one table, there was a familiar object, on the other table, there was a novel object (drawn for the purpose of the study). The speaker requested an object by saying "Oh cool, there is a [non-word] on the table, how neat, can you give me the [non-word]?". Children responded by touching one of the objects. The location of the novel object (left or right table) and the animal character were counterbalanced. Each child received 12 trials, one with each familiar object. The novel object also changed from trial to trial. We coded as correct choice if children chose the novel object as the referent of the novel word.

```{r fig1,echo = F, fig.align = "center", fig.cap = "Schematic experimental procedure with screenshots from the experiments.", out.width="100%"}
knitr::include_graphics("../graphs/method_overview.png")
```

Each child completed 12 trials, each with a different familiar and a different novel object. Familiar objects were selected to vary along the dimension of how likely children were to know the word for each object. This including objects that most 2-year-olds could name (e.g. a duck) as well as objects that only very few 5-year-olds could name (e.g. a pawn). The selection was based on age of acquisition ratings from Kuperman and colleagues [-@kuperman2012age]. While these ratings do not capture the absolute age when children acquire these words, they capture the relative order in which words are learned. Figure \@ref(fig:fig2)A shows the objects used in the experiment. We induced this variation to estimate the role of semantic knowledge in a mutual exclusivity inference.

```{r, include = F}
plot_aoa_ratings <- aoa_ratings%>%
  mutate(image = paste("../experiments/kids/images/",item,".png", sep=""))

plot_aoa <- ggplot(plot_aoa_ratings, aes(x = reorder(item, mean_aoa), y = mean_aoa)) +
  geom_point(size =2, pch = 4)+
  ylab("Mean rated age of acquisition")+
  xlab("Object")+
  ylim(0,15)+
  geom_image(aes(image=image, y = mean_aoa+2), asp = 4)+
  theme_light()+
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### Results

```{r table1, echo=T}
chance_me <- me_data %>%
  group_by(subage, subid) %>%
  summarise(correct = mean(correct)) %>%
  summarise(correct = list(correct)) %>%
  group_by(subage)%>%
  mutate(Mean= round(mean(unlist(correct)),2),
         BayesFactor = format(round(extractBF(ttestBF(unlist(correct), mu = 0.5))$bf), scientific = F),
         `Age group` = subage)%>%
  ungroup()%>%
  select(`Age group`, Mean, BayesFactor)

knitr::kable(chance_me, caption = "Proportion of children choosing the novel object compared to a level expected by chance based on a one sample Bayesian t-test. Responses are aggregated for each participant across familiar objects.", digits = 2, align = "l")
```

As a first step, we evaluated whether children made a mutual exclusivity inference. For this analysis, we aggregated participants' responses across familiar objects. We used the function `ttestBF` from the R-package `BayesFactor` [@R-BayesFactor] to compute a Bayes factor (BF) in favor of the hypothesis that children chose the novel object more often than expected by chance (50% correct). Table \@ref(tab:table1) shows that all age groups made the inference.

```{r, echo=T}
# prior_me <- c(prior(normal(0, 5), class = Intercept),
#            prior(normal(0, 5), class = b),
#            prior(cauchy(0, 1), class = sd))
# 
# 
# bm_me <- brm(correct ~ age + (1|subid) + (age | item) + (age | agent),
#                     data = me_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99, max_treedepth = 20),
#           sample_prior = F,
#           prior = prior_me,
#           cores = 4,
#           chains = 4,
#           iter = 5000)%>%
#   saveRDS(.,"../saves/bm_me.rds")
# 
# 
# bm_me2 <- brm(correct ~ age + (1|subid) + (age | agent),
#                     data = me_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99, max_treedepth = 20),
#           sample_prior = F,
#           prior = prior_me,
#           cores = 4,
#           chains = 4,
#           iter = 5000)%>%
#   saveRDS(.,"../saves/bm_me.rds")

bm_me <- readRDS("../saves/bm_me.rds")

bm_me2 <- readRDS("../saves/bm_me2.rds")

```{r}
fixef_me <- as_tibble(fixef(bm_me), rownames = "term")

ranef_me <-  ranef(bm_me)

ranef_plot_me <- as_tibble(ranef_me$item, rownames = "item")%>%
  mutate(grand_intercept = fixef_me%>%filter(term=="Intercept")%>%pull(Estimate),
         grand_slope = fixef_me%>%filter(term=="age")%>%pull(Estimate))%>%
  group_by(item) %>%
  tidyr::expand(Estimate.Intercept,Estimate.age,grand_intercept,grand_slope, age = unique(me_data$age))%>%
  mutate(y = plogis(grand_intercept + Estimate.Intercept+(Estimate.age+grand_slope)*age), 
         age = age+min(me_data$age_num))%>%
  left_join(aoa_ratings)%>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(item), mean_aoa))

plot_me <- ggplot(ranef_plot_me, aes(x=age,y = y, col = item))+
  geom_hline(yintercept = 0.5, lty=2)+
  geom_jitter(data = me_data%>%left_join(aoa_ratings), aes(x = age_num, y = correct, col = reorder(item, mean_aoa)), width = 0, height = 0.02, alpha = .2)+
  geom_line(size = 1)+
  labs(x="Age",y="Mutual exclusivity effect")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_viridis_d(name = "Object")

cor_plot_me <- as_tibble(ranef_me$item, rownames = "item") %>%
  left_join(aoa_ratings)%>%
  ggplot(., aes(x = mean_aoa, y = Estimate.Intercept))+
  geom_abline(intercept = 1, slope = -1, lty = 2, alpha = 1, size = .5)+
  geom_point(pch = 4, size = 2)+
  geom_smooth(method = "lm", col = "black", se = F, lty = 2, size = .5)+
  xlab("Rated age of acquisition")+
  ylab("Mutual exclusivity effect (model intercept)")+
  ylim(-1,1)+
  stat_cor(method = "pearson", label.x = 7, label.y = .99)+
  theme_few()
```

As a second step, we investigated how the inference changed as a function of age and the familiar object. We modeled the trial by trial data using a Bayesian generalized linear mixed model (GLMM). We used the function `brm` from the package `brms` [@R-brms_a]. We pre-registered the use of default priors in all models. However, the model in Experiment 3 was unable to initialize with default priors and we thus used weakly informative priors for all models to be consistent. The priors we used were `normal(0,5)` for fixed effects and `cauchy(0,1)` for standard deviations of random effects.  The model formula was `correct ~ age + (1 | id) + (age | object) + (age | agent)`. That is, we modeled an overall slope for age (continuous, anchored at the minimum) and the object specific developmental trajectories as deviations from the overall intercept and slope (random effects). We did not pre-register agent as a random effect, but retrospecitvely included it to be consistent with Experiment 2 and 3.

The estimate for age was positive and reliably different from zero (*$\beta$* = `r fixef_me%>%filter(term == "age")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_me%>%filter(term == "age")%>%pull(Q2.5)%>%round(2)` - `r fixef_me%>%filter(term == "age")%>%pull(Q97.5)%>%round(2)`). Older children were more likely to make a mutual exclusivity inference. To assess the variability accross objects, we compared the fit of the above model to a model lacking `object` as a random effect. Following McElreath [-@rethinking], we compared models using WAIC (widely applicable information criterion) scores and weights. The WAIC score is an indicator of the model’s predictive accuracy for out of sample data; model’s with lower scores are preferred. WAIC weights are an estimate of the probability that this model (compared to all other models considered) will make the best predictions on new data. The model including object provided a much better fit compared to the model lacking it (see Table \@ref(tab:table2)). Figure \@ref(fig:fig2)B visualizes the model based developmental trajectory for each familiar object and illustrates the substantial variation between them, both in terms of absolute strength of the inference as well as its developmental trajectory. Figure \@ref(fig:fig2)C shows the correlation between rated age of acquisition and object specific model intercept. The mutual exclusivity effect was stronger for words that were rated to be acquired earlier. Objects for which children were less likely to know the word produced a weaker mutual exclusivity effect. Taken together, the strength  of the mutual exclusivity inference depended on age as well as the familiar object.

```{r table2, echo=T}

me_waic <- brms::waic(bm_me, bm_me2, compare = F)

me_weights <- model_weights(bm_me, bm_me2, weights = "waic")

me_comp <- tibble(
  Model = c("with object as RE", "without object as RE"),
  WAIC = round(c(me_waic$loos$bm_me$estimates["waic","Estimate"],me_waic$loos$bm_me2$estimates["waic","Estimate"]),2),
  SE = round(c(me_waic$loos$bm_me$estimates["waic","SE"],me_waic$loos$bm_me2$estimates["waic","SE"]),2),
  weight = round(c(me_weights[1],me_weights[2]))
)

knitr::kable(me_comp, caption = "Model comparison in experiment 1 based on WAIC scores and weights.", digits = 2, align = "l")
```

```{r fig2, include = T, fig.align = "center", fig.cap = "A:Familiar words and corresponding pictures by rated age of acquisition. B: Developmental trajectories of mututal exclusivity effect by familiar object based on the mean of the model posterior distribution. Dots show individual datapoints. Lighter colors indicate later rated age of acquisition. Dotted line indicates a level of performance expected by chance. C: Correlation between rated age of acquisiton and mutual exclusivity effect (model based intercept for each familiar object).", fig.width=12, fig.height = 4}
ggarrange(plot_aoa, plot_me, cor_plot_me,  labels = c("A","B","C"), nrow = 1, widths = c(1,1.3,1))
```

## Experiment 2: Common ground

Here we tested children's sensitivity to common ground that is build up over the course of a conversation. In particular, we tested whether children keep track of which object is new to a speaker and which they have encountered previously [@akhtar1996role; @diesendruck2004two]. The main goal of the experiment was to measure how children's sensitivity to common ground changes with age.

The experiment was preregistered at https://osf.io/au5hr. The experiment itself can be run by downloading the associated repository and opening the file `experiments/kids/kids_novel.html`.

### Participants

We tested `r length(unique(prior_data$subid))` children from the same general population as in Experiment 1, including `r length(unique(prior_data$subid[prior_data$subage == 2]))` 2-year-olds (range = `r format(round(min(prior_data$age_num[prior_data$subage == 2]),2), nsmall = 2)` - `r format(round(max(prior_data$age_num[prior_data$subage == 2]),2), nsmall = 2)`, 7 girls), `r length(unique(prior_data$subid[prior_data$subage == 3]))` 3-year-olds (range = `r format(round(min(prior_data$age_num[prior_data$subage == 3]),2), nsmall = 2)` - `r format(round(max(prior_data$age_num[prior_data$subage == 3]),2), nsmall = 2)`, 14 girls) and  `r length(unique(prior_data$subid[prior_data$subage == 4]))` 4-year-olds (range = `r format(round(min(prior_data$age_num[prior_data$subage == 4]),2), nsmall = 2)` - `r format(round(max(prior_data$age_num[prior_data$subage == 4]),2), nsmall = 2)`, 14 girls). Data from 5 additional children was not included because they were either exposed to less than 75% of English at home (3) or the technical equipment failed (2).

### Procedure

The general setup was the same as in Experiment 1. The speaker was positioned between the tables. There was a novel object (drawn for the purpose of the study) on one of the tables while the other table was empty. Next, the speaker turned to one of the tables and either commented on the presence ("Aha, look at that.") or the absence ("Hm, nothing there") of an object. Then the speaker disappeared. While the speaker was away, a second novel object appeared on the previously empty table. Then the speaker returned and requested an object in the same way as in Experiment 1 (see also Figure \@ref(fig:fig1)B). The positioning of the novel object in the beginning of the experiment as well as the location the speaker turned to first was counterbalanced. Children received five trials, each with a different pair of novel objects. We coded as correct choice if children chose the object that was new to the speaker as the referent of the novel word.

### Results

```{r table3, echo=T}
chance_prior <- prior_data %>%
  group_by(subage, subid) %>%
  summarise(correct = mean(correct)) %>%
  summarise(correct = list(correct)) %>%
  group_by(subage)%>%
  mutate(Mean= round(mean(unlist(correct)),2),
         BayesFactor = format(round(extractBF(ttestBF(unlist(correct), mu = 0.5))$bf,2), scientific = F),
         `Age group` = subage)%>%
  ungroup()%>%
  select(`Age group`, Mean, BayesFactor)

knitr::kable(chance_prior, caption = "Proportion of children choosing the object that was new to the speaker compared to a level expected by chance based on a one sample Bayesian t-test. Responses are aggregated for each participant across trials.", digits = 2, align = "l")
```

Table \@ref(tab:table3) compares children's correct responses to a level expected by chance (50%). We found evidence that, as a group, 3- and 4-year-olds, but not 2-year-olds, inferred that the novel word referred to the object that was new to the speaker.

```{r, echo=T}
# prior_cg <- c(prior(normal(0, 5), class = Intercept),
#            prior(normal(0, 5), class = b),
#            prior(cauchy(0, 1), class = sd))
# 
# 
# bm_cg <- brm(correct ~ age + (1|subid) + (age | agent),
#                     data = prior_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99, max_treedepth = 20),
#           sample_prior = F,
#           prior = prior_cg,
#           cores = 4,
#           chains = 4,
#           iter = 5000)%>%
#   saveRDS(.,"../saves/bm_cg.rds")

bm_cg <- readRDS("../saves/bm_cg.rds")
```

```{r}
fixef_cg <- as_tibble(fixef(bm_cg), rownames = "term")

plot_cg_data <- prior_data %>%
  group_by(age_num, subid) %>%
  summarise(correct = mean(correct))

plot_cg_samples <- posterior_samples(bm_cg, "^b", subset = 1:200)%>%
  mutate(sample = 1:length(b_age))%>%
  expand_grid(.,unique(prior_data$age))%>%
  mutate(age = `unique(prior_data$age)`,
         y =  plogis(b_Intercept + b_age * age))%>%
  select(-`unique(prior_data$age)`)

plot_cg_map <- as_tibble(fixef(bm_cg), rownames = "term")%>%
  select(term, Estimate)%>%
  spread(term, Estimate)%>%
  expand_grid(.,unique(prior_data$age))%>%
  mutate(slope = age, 
         age = `unique(prior_data$age)`,
         y =  plogis(Intercept + slope * age))%>%
  select(-`unique(prior_data$age)`)

plot_cg <- ggplot() +
  geom_hline(yintercept = 1/2, lty=2, size = 1)+
  geom_jitter(data = plot_cg_data,aes(x = age_num, y= correct), width = .00, height = .01, alpha = .5)+
  geom_line(data = plot_cg_samples, aes(x = age+min(prior_data$age_num), y = y, group = sample), size = .025)+
  geom_line(data = plot_cg_map, aes(x =age+min(prior_data$age_num), y = y), size = 1)+
  labs(x="Age",y="Proportion object new to speaker chosen")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)

To directly investigate whether children's response changed with age, we modeled the trial by trial data using a Bayesian GLMM (formula: `correct ~ age + (1 | id) + (age | speaker)`, specifications see [Experiment 1](#experiment-1-mutual-exclusivity)). The estimate for age was positive and reliably different from zero (*$\beta$* = `r fixef_cg%>%filter(term == "age")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_cg%>%filter(term == "age")%>%pull(Q2.5)%>%round(2)` - `r fixef_cg%>%filter(term == "age")%>%pull(Q97.5)%>%round(2)`, see Figure \@ref(fig:fig3)A). Older children were more likely to chose the object that was new to the speaker as the referent of the novel word, suggesting that the sensitivity to common ground in this context increases with age.

## Experiment 3: Integration

Experiment 3 combined the procedures from Experiment 1 and 2. As a consequence, children had to consider not just their semantic knowledge of the word for the familiar object and the inference this licences but also the role that each object (novel and familiar) had played in the preceding interaction. Combining the two procedures created two conditions: In the *congruent* condition, the novel object was also the object that was new to the speaker. In this case, the mutual exclusivity inference as well as the common ground inference pointed to the novel object as the referent. In the *incongurent condition*, the familiar object was new to the speaker. Int his case, the two inferences pointed to different objects. The main focus of the overall study was to model how children integrate and balance these different information sources. We investigate this question in depth in the [modelling](#model) section below. Here, we limit the discussion to whether children differentiated between the two conditions.

The experiment was preregistered at https://osf.io/4nm8g. The experiment itself can be run by downloading the associated repository and opening the file `experiments/kids/kids_combination.html`.

### Participants

We tested `r length(unique(comb_data$subid))` children from the same general population as in Experiment 1 and 2, including `r length(unique(comb_data$subid[comb_data$subage == 2]))` 2-year-olds (range = `r format(round(min(comb_data$age_num[comb_data$subage == 2]),2), nsmall = 2)` - `r format(round(max(comb_data$age_num[comb_data$subage == 2]),2), nsmall = 2)`, 7 girls), `r length(unique(comb_data$subid[comb_data$subage == 3]))` 3-year-olds (range = `r format(round(min(comb_data$age_num[comb_data$subage == 3]),2), nsmall = 2)` - `r format(round(max(comb_data$age_num[comb_data$subage == 3]),2), nsmall = 2)`, 14 girls) and  `r length(unique(comb_data$subid[comb_data$subage == 4]))` 4-year-olds (range = `r format(round(min(comb_data$age_num[comb_data$subage == 4]),2), nsmall = 2)` - `r format(round(max(comb_data$age_num[comb_data$subage == 4]),2), nsmall = 2)`, 14 girls). Data from 20 additional children was not included because they were either exposed to less than 75% of English at home (15), did not finish at least half of the test trials (3) or the technical equipment failed (2).

### Procedure

Experiment 3 followed the same procedure as Experiment 2 but involved the same objects as Experiment 1. In the beginning, one table was empty while there was an object (novel or familiar) on the other one. After commenting on the presence or absence of an object on each table, the speaker disappeared and a second object appeared (familiar or novel). Next, the speaker re-appeared and made the usual request.

In the congruent condition, the familiar object was present in the beginning and the novel object appeared while the speaker was away (Figure \@ref(fig:fig1)C - left). In this case, both the mutual exclusivity and the common ground inference pointed to the novel object as the referent. In the incongruent condition, the novel object was present in the beginning and the familiar object appeared later. In this case, the two inferences pointed to different objects (Figure \@ref(fig:fig1)C - right).

Participants received up to 12 test trials, six in each condition, each with a different familiar and novel object. Familiar objects were the same as in Experiment 1. The positioning of the objects on the tables and the location the speaker first turned to were counterbalanced. Participants could stop the experiment after six trials (three per condition). If a participant stopped after half of the trials, we tested an additional participant to reach a pre-registered number of data points per cell.

### Results

All results are reported from the perspective of the mutual exclusivity inference (`correct` in the model formula below). In the incongruent condition, high proportions speak to a mutual exclusivity inference and low proportion for a common ground inference. In the congruent condition, both inferences pointed in the same direction. The focus of this experiment was on information integration and we therefore did not compare the performance to chance.

```{r, echo=T}

# prior_comb <- c(prior(normal(0, 5), class = Intercept),
#            prior(normal(0, 5), class = b),
#            prior(cauchy(0, 1), class = sd))
# 
# bm_comb <- brm(correct ~ age * alignment + (alignment | subid) + (age * alignment | item)+ (age * alignment | agent),
#                     data = comb_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99, max_treedepth = 20),
#           sample_prior = F,
#           prior = prior_comb,
#           cores = 4,
#           chains = 4,
#           inits = 0,
#           iter = 5000)%>%
#   saveRDS(.,"../saves/bm_comb.rds")
# 
# bm_comb2 <- brm(correct ~ age * alignment + (alignment | subid) + (age * alignment | agent),
#                     data = comb_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99, max_treedepth = 20),
#           sample_prior = F,
#           prior = prior_comb,
#           cores = 4,
#           chains = 4,
#           inits = 0,
#           iter = 5000)%>%
#   saveRDS(.,"../saves/bm_comb2.rds")

bm_comb <- readRDS("../saves/bm_comb.rds")

bm_comb2 <- readRDS("../saves/bm_comb2.rds")

```{r}
fixef_comb <- as_tibble(fixef(bm_comb), rownames = "term")

ranef_comb <-  ranef(bm_comb)

plot_comb_map <- bind_rows(
  as_tibble(ranef_comb$item, rownames = "item")%>%
  mutate(condition = "congruent",
         condition_code = 0),
  as_tibble(ranef_comb$item, rownames = "item")%>%
  mutate(condition = "incongruent",
         condition_code = 1))%>%
  mutate(grand_intercept = fixef_comb%>%filter(term=="Intercept")%>%pull(Estimate),
         grand_age = fixef_comb%>%filter(term=="age")%>%pull(Estimate),
         grand_cond = fixef_comb%>%filter(term=="alignmentincongruent")%>%pull(Estimate),
         grand_intact = fixef_comb%>%filter(term=="age:alignmentincongruent")%>%pull(Estimate))%>%
  group_by(item, condition, condition_code)%>%
  expand_grid(. ,age = unique(comb_data$age))%>%
  mutate(y = plogis(grand_intercept + 
                      Estimate.Intercept +
                      grand_cond * condition_code +
                      Estimate.alignmentincongruent * condition_code +
                      grand_age * age +
                      Estimate.age * age +
                      grand_intact * (condition_code * age) +
                      `Estimate.age:alignmentincongruent` * (condition_code * age)),
         age = age+min(comb_data$age_num))%>%
  left_join(aoa_ratings)%>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(item), mean_aoa))

plot_comb <- ggplot(plot_comb_map, aes(x=age,y = y, col = item))+
  geom_hline(yintercept = 0.5, lty=2)+
  geom_jitter(data = comb_data%>%left_join(aoa_ratings)%>%ungroup()%>%mutate(item = fct_reorder(factor(item), mean_aoa)), aes(x = age_num, y= correct, col = item), width = .00, height = .04, alpha = .2)+
  geom_line(size = 1)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  facet_grid(~condition)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_viridis_d(name = "Object")

We modeled the trial by trial data in the following way: `correct ~ age * alignment + (alignment | subid) + (age * alignment | item) + (age * alignment | agent)`. We pre-registered to include item as a fixed effect in Experiment 3. The corresponding model was too complex to be constrained by the data. Furthermore, as explained in Experiment 1, items were chosen based on their rated age of acquisition. That is, we assumed that they are not necessarily different kinds but that they represent different locations on a distribution of required semantic knowledge. For further model specifications see [Experiment 1](#experiment-1-mutual-exclusivity)).

The estimate for age was reliably positive (*$\beta$* = `r fixef_comb%>%filter(term == "age")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_comb%>%filter(term == "age")%>%pull(Q2.5)%>%round(2)` - `r fixef_comb%>%filter(term == "age")%>%pull(Q97.5)%>%round(2)`). The incongruent condition had a strong negative impact (*$\beta$* = `r fixef_comb%>%filter(term == "alignmentincongruent")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_comb%>%filter(term == "alignmentincongruent")%>%pull(Q2.5)%>%round(2)` - `r fixef_comb%>%filter(term == "alignmentincongruent")%>%pull(Q97.5)%>%round(2)`), showing that children differentiated between the two conditions. The interaction term was weakly - though not entirely - negative, suggesting a shallower slope for age in the incongruent condition (*$\beta$* = `r fixef_comb%>%filter(term == "age:alignmentincongruent")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_comb%>%filter(term == "age:alignmentincongruent")%>%pull(Q2.5)%>%round(2)` - `r fixef_comb%>%filter(term == "age:alignmentincongruent")%>%pull(Q97.5)%>%round(2)`). A model lacking `object` as a random effect provided a much poorer fit, suggesting substantial variation across objects (see Table \@ref(tab:table4)). Figure \@ref(fig:fig3)B visualizes the model. Taken together, the results show that children responded to the way the two inferences were aligned with one another.

```{r table4, echo=T}

comb_waic <- brms::waic(bm_comb, bm_comb2, compare = F)

comb_weights <- model_weights(bm_comb, bm_comb2, weights = "waic")

comb_comp <- tibble(
  Model = c("with object as RE", "without object as RE"),
  WAIC = round(c(comb_waic$loos$bm_comb$estimates["waic","Estimate"],comb_waic$loos$bm_comb2$estimates["waic","Estimate"]),2),
  SE = round(c(comb_waic$loos$bm_comb$estimates["waic","SE"],comb_waic$loos$bm_comb2$estimates["waic","SE"]),2),
  weight = round(c(comb_weights[1],comb_weights[2]))
)

knitr::kable(comb_comp, caption = "Model comparison in experiment 3 based on WAIC scores and weights.", digits = 2, align = "l")
```

```{r fig3, include = T, fig.align = "center", fig.cap = "Proportion of choosing the object that was new to the speaker by age. Dots show the mean response for each participant. The solid black line shows the developmental trajectory based on the mean of the model posterior distribution. Lighter lines show 200 random draws from the posterior distribution to depict uncertainty. Dotted line indicates a level of performance expected by chance.", fig.width=12, fig.height = 4}
ggarrange(plot_cg, plot_comb,  labels = c("A","B"), nrow = 1, widths = c(1,2))
```

## Discussion

The experiments reported above show that children are sensitive to the types of information sources we intended to manipulate. Experiment 1 showed that children of all age groups are make a mutual exclusivity inference, that the strength of this inference increases with age and, crucially, that it depends on the type of familiar object that is presented. Experiment 2 showed that three- and four-year-olds are sensitive the common ground manipulation we implemented and that this inference increases with age. Finally, experiment 3 showed that children respond differently depending on how the mutual exclusivity inference and the common ground inference are aligned with one another. In the next section, we use Bayesian cognitive models to address the question of *how* information sources are integrated when the two inferences are combined with one another.

# Models

The main purpose of the study was to study *how* children integrate different information sources during word learning and how this process develops with age. To do so, we use Bayesian cognitive models of pragmatic reasoning. We first describe an *integration model* which we think best represents the inference and integration processes and then specify how this model captures developmental change. Next, we ask how well this model *predicts* how children integrate the two information sources. That is, in a situation in which we know the development trajectories for the mutual exclusivity inference as well as for the common ground inference, what can we say about what happens when common ground and mutual exclusivity are combined. We then test the predictive power of the model by comparing the model predictions to the data from experiment 3. We use formal model comparison methods to test the *integration model* against a range of alternative models.

Finally, we ask how well our model *explains* the way that children integrate the two information sources. For this analysis, we fit the free parameters in the model to all the available data, those from experiment 1 and 2 as well as the integration data from experiment 3. We then compare the model to a range of alternative models that make different assumptions about how information is integrated and how this process develops. This approach answers the question of how we can best explain how children integrate the different information sources.

## Modeling framework

The cognitive models are situated in the Rational Speech Act (RSA) framework [@frank2012predicting; @goodman2016pragmatic]. RSA models are models of pragmatic reasoning in that they treat language understanding as a special case of Bayesian social reasoning. A listener interprets an utterance by assuming it was produced by a cooperative speaker who had the goal to be informative. Being informative is defined as providing a message that would increase the probability of the listener inferring the speaker’s intended message. This notion of contextual informativeness captures the Gricean idea of cooperation between speaker and listener.

Our model describes a listener jointly reasoning about the referent of a speaker's utterance and trying to learn a lexicon (object--word mappings). This reasoning is contextualized by the prior probability of each referent. This prior probability is thought to be a function of the common ground shared between speaker and listener in that interacting around the objects changes the probability that they will be referred to later. We assume that the degree to which interactions around objects are integrated into the common ground and thus change the prior probability of those objects depends on the child's age.

To decide between referents, the listener reasons about what a rational speaker would say given an intended referent. This speaker is assumed to compute the informativity of for each available utterance and then choose the most informative one. However, this expectation of speaker informativeness may vary and is captured by the parameter $\alpha$. In particular, we take $\alpha$ to be a function of the child's age.

The informativity of each utterance is given by imagining which referent a literal listener, who interprets words according to their literal semantics, would infer upon hearing the utterance. Thus, this reasoning depends on what kind of semantic knowledge (word--object mappings) the speaker thinks the literal listener knows. We assume that a listener's knowledge of a word's semantics is graded (not categorical). That is, for each object involved there is a probability $p$ that the literal listener knows the word for it. For each of the novel objects, this semantic knowledge is 0, which assumes that the novel word is equaliy likely to refer to the novel object as it is to refer to the familiar object. For familiar objects, semantic knowledge is a function of the degree-of-acquisition of the associated word, which in turn depends upon the kind of object (its expected acquisition trajectory) as well as on the child's age.

## Loci of development

The model description above points to three potential loci of developmental change: semantic knowledge, expectations about speaker informativeness and sensitivity to common ground. Each of theses components is represented by a parameter that plays a particular functional role in the model. We capture developmental change by making these parameters a function of age and therefore estimating a developmental trajectory (intercept and slope) for each parameter.

### Semantic knowledge

Semantic knowledge captures the degree of certainty with which the naive listener is assumed to know the label for the familiar object. As a consequence, semantic knowledge differs between familiar objects. For objects whose labels are generally acquired earlier (e.g. carrot) semantic knowledge should generally be high whereas for others (e.g. pawn) semantic knowledge should generally be lower. However, semantic knowledge also varies with age such that older children are more likely to know the labels for more of the familiar objects compared to younger children. As a consequence, each familiar object has a unique developmental trajectory with respect to semantic knowledge. Technically, the object-specific parameters are estimated in the form of a hierarchical regression (mixed-effects) model; that is, each object's trajectory is estimated as a deviation from an overall trajectory of vocabulary development. This overall (vocabulary) trajectory represents the development of semantic knowledge that is independent of a particular familiar object--label pairing.

(MH: This paragraph is opaque)
Semantic knowledge enters the likelihood term of the model specified above. The likelihood depends not just on the parameter settings for semantic knowledge but also on the value of the parameter capturing expectations about speaker informativeness ($\alpha$ - see next section). As a consequence, these parameters are jointly estimated and co-vary with one another.

### Expectations about speaker informativeness

>>>>

---
title: "Word learning at the semantics pragmatics interface"
output: html_document
---

```{r, include = F}
library(tidyverse)
library(rwebppl)
library(gridExtra)
library(coda)
library(ggthemes)
library(readxl)
library(ggpubr)
library(stringr)
library(matrixStats)
library(data.table)
library(langcog)
library(ggimage)
library(BayesFactor)

library(cowplot)
library(magick)

@@
